Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex
added caption to rl

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
  \setlength{\figurewidth}{.28\textwidth}
  \setlength{\figureheight}{\figurewidth}
 \begin{subfigure}{.78\textwidth}
   % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
   % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{Add caption.}
 \label{fig:rl}
\end{figure}

>>>>

 \end{tikzpicture}}
 \end{subfigure}
 \hfill
  \setlength{\figurewidth}{.28\textwidth}
  \setlength{\figureheight}{\figurewidth}
 \begin{subfigure}{.78\textwidth}
   % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
   % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
   \input{./fig/rl.tex}
 \end{subfigure}
 \hfill
 \caption{\textbf{Reinforcement learning experiments} Training curves showing that our model's uncertainty estimates improve sample efficiency in RL.
   Our method (blue/green) converges to the optimal solution in fewer environment steps than the baseline model-based RL method (magenta) and (DDPG) the model-free baseline  (yellow).}
 \label{fig:rl}
\end{figure}
